Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-02 manuscript.Rmd
Compute direct distance from Washington Monument

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

>>>>

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)

# Compute distance from Washington Monument
mnm <- tribble(
  ~latitude, ~longitude,
  38.8895, -77.0353
)

mnm_sf <- mnm %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326) %>%
  st_transform(crs = 102285)

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE))
```
